Why robot programming is hard

### 2013-07-19 paper.tex
Version 2 shipped.

\begin{figure*}[tbh]
\center\scalebox{0.20}{\includegraphics{rviz.png}}
\caption{RViz interface for controlling robots}
\label{rviz}
\end{figure*}

@@

Robots are complex beings full of many moving parts. For example, Willow Garage's robotic research platform, the PR-2, has two independently controlled 7-DOF arms, a head that can pan and tilt, a torso that can be raised and lowered, and a base that can move and turn in all directions. Each of these parts must be controlled independently in order to orchestrate a desired robotic behavior.

End user programming systems have tried to simplify the problem of concurrency. One approach used is visualizing the different components on a timeline. This approach is popular with media creation tools such as Apple's GarageBand or Autodesk's 3D Studio Max. A second paradigm, taken by visual programming languages such as Scratch, makes the notion of time a global constant and runs all blocks of user code simultaneously in the virtual environment. More research is needed to discover what paradigm works best for controlling robot parts concurrently.

Even if individual robot parts can be programmed to act in parallel, there will still be a need for reasoning about concurrent robot behavior at a higher level. One form this will take is for background tasks, such as specifying that a robot should try to tidy up the room in between (or during) its other assigned chores. Supporting high level concurrency will introduce new problems, such as task prioritization (should it interrupt its task of bringing you a beer to clean up a wine spill on carpet?).

@@

@@

Robot programming environments are beginning to address these challenges and produce useful systems that can be controlled by untrained users. The key tradeoff is simplicity versus expressiveness: in order to make systems that are more tractable for novices, they need to simplify key aspects of the robot's behavior, thereby sacrificing its ability to perform a full range of behavior.

@@

Roboticists are hard at work developing increasingly autonomous robot capabilities for well-specified tasks such as 2D navigation (getting from point A to point B within a building), arm motion planning (moving the gripper to a specified position and orientation while avoiding obstacles), and recognizing and picking up discrete objects on a flat surface. Autonomy is key for enabling robots to automatically perform longer and more complex tasks on their own, but it also reduces expressivity by limiting the ways in which those tasks can be performed to those that are programmed in to the automation.

@@

We have made use of these autonomous functions to develop a system at Willow Garage called Continuous Ops that enables casual users to control our PR-2 robots through a web interface (Figure~\ref{contops}). This web interface, accessible from standard laptops or tablets, provides the ability to tell a PR-2 robot to unplug itself from the power supply, navigate autonomously to anywhere in the buliding, position itself in front of a table, automatically identify graspable objects on that table, and pick up an object.

>>>>

\begin{figure*}[tbh]
\center\scalebox{0.20}{\includegraphics{rviz.png}}
\caption{RViz interface for robot visualization}
\label{rviz}
\end{figure*}

@@

@@

Robots are complex beings full of many moving parts. For example, Willow Garage's PR-2 has two independently controlled 7-DOF arms, a head that can pan and tilt, a torso that can be raised and lowered, and a base that can move and turn in all directions. Robots are also equipped with a slew of sensors including cameras, depth sensors, laser rangefinders, touch sensors, and feedback about its electrical and motor systems. Sensors and actuators must be operated together in coordination to produce a desired robotic behavior.

End user programming systems have tried to simplify the problem of concurrency. Some systems visualize the different components on a timeline. This approach is popular with media creation tools such as Apple's GarageBand or Autodesk's 3D Studio Max. A second paradigm, taken by visual programming languages such as Scratch~\cite{scratch}, makes the notion of time a global constant and runs all blocks of user code simultaneously in the virtual environment. More research is needed to discover what paradigm works best for controlling robot parts concurrently.

Even if individual robot parts can be programmed to act in parallel, there will still be a need for reasoning about concurrent robot behavior at a higher level. One form this will take is for background tasks, such as specifying that a robot should try to tidy up the room in between (or during) its other assigned chores. Supporting high level concurrency will introduce new problems, such as task prioritization (is the current task of bringing you a beer more important than cleaning up the wine spill it just detected?).

@@

Robot programming environments are beginning to address all of these challenges and produce useful systems that can be controlled by untrained users. The key tradeoff is simplicity versus expressiveness: in order to make systems that are more tractable for novices, they need to simplify key aspects of the robot's behavior, thereby sacrificing its ability to perform a full range of behavior.

@@

Roboticists are hard at work developing increasingly autonomous robot capabilities for well-specified tasks such as 2D navigation (getting from point A to point B within a building), arm motion planning (moving the gripper to a specified position and orientation while avoiding obstacles)\footnote{MoveIt!, http://moveit.ros.org}, and recognizing and picking up discrete objects on a flat surface. Autonomy is key for enabling robots to automatically perform longer and more complex tasks on their own.

@@

\begin{figure*}[tbh]
\center\scalebox{0.40}{\includegraphics{contops.png}}
\caption{Continuous Ops interface for picking up objects on a table}
\label{contops}
\end{figure*}

We have made use of these autonomous functions to develop a system at Willow Garage called Continuous Ops (short for ``Continuous Operations'') that enables casual users to control our PR-2 robots through a web interface (Figure~\ref{contops}). This web interface, accessible from standard laptops or tablets, provides the ability to tell a PR-2 robot to unplug itself from the power supply, navigate autonomously to anywhere in the buliding, position itself in front of a table, automatically identify graspable objects on that table, and pick up an object.
